\documentclass{tufte-handout}
\let\orignewcommand\newcommand  % store the original \newcommand
\let\newcommand\providecommand  % make \newcommand behave like \providecommand
\RequirePackage{verse}
\let\newcommand\orignewcommand  % use the original `\newcommand` in future
\makeatletter
% Use the original definition from verse.sty
\renewcommand*{\theHpoemline}{\arabic{verse@envctr}.\arabic{poemline}}
\makeatother

% Set up the spacing using fontspec features
% See https://groups.google.com/d/topic/tufte-latex-commits/JcgGP-1R138/discussion
   \renewcommand\allcapsspacing[1]{{\addfontfeature{LetterSpace=15}#1}}
   \renewcommand\smallcapsspacing[1]{{\addfontfeature{LetterSpace=10}#1}}

%\geometry{showframe}% for debugging purposes -- displays the margins

\usepackage{amsmath}

%%
% Prints a trailing space in a smart way.
\usepackage{xspace}

% Set the main and monospaced fonts
%
\setromanfont[Mapping=tex-text,Ligatures={Common, Rare, Discretionary},Numbers=OldStyle]{Adobe Caslon Pro}
\setmonofont[Mapping=tex-text,Scale=MatchLowercase]{Triplicate T4c}

% Set up the images/graphics package
\usepackage{graphicx}
\setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
\graphicspath{{graphics/}}

\title{En Route}
\author{J. Brander Matthews}
\date{Sunday, September 20th, 2015}  % if the \date{} command is left out, the current date will be used

% The following package makes prettier tables.  We're all about the bling!
\usepackage{booktabs}

% The units package provides nice, non-stacked fractions and better spacing
% for units.
\usepackage{units}

% The fancyvrb package lets us customize the formatting of verbatim
% environments.  We use a slightly smaller font.
\usepackage{fancyvrb}
\fvset{fontsize=\normalsize}

% Small sections of multiple columns
\usepackage{multicol}

% Provides paragraphs of dummy text
\usepackage{lipsum}

% Make hyperlinks appear as footnotes
% Taken from https://groups.google.com/forum/#!topic/pandoc-discuss/O-N0H1eBnVU
\usepackage{url}
% This bit ensures hyperlinks can have linebreaks on hyphens
% see http://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother
\renewcommand{\href}[2]{#2\footnote{\raggedright\url{#1}}}
% optionally add \itshape to get italics, or replace \rmfamily with \ttfamily
\renewcommand\UrlFont{\rmfamily\itshape}

% These commands are used to pretty-print LaTeX commands
\newcommand{\doccmd}[1]{\texttt{\textbackslash#1}}% command name -- adds backslash automatically
\newcommand{\docopt}[1]{\ensuremath{\langle}\textrm{\textit{#1}}\ensuremath{\rangle}}% optional command argument
\newcommand{\docarg}[1]{\textrm{\textit{#1}}}% (required) command argument
\newenvironment{docspec}{\begin{quote}\noindent}{\end{quote}}% command specification environment
\newcommand{\docenv}[1]{\textsf{#1}}% environment name
\newcommand{\docpkg}[1]{\texttt{#1}}% package name
\newcommand{\doccls}[1]{\texttt{#1}}% document class name
\newcommand{\docclsopt}[1]{\texttt{#1}}% document class option name

\begin{document}

\maketitle% this prints the handout title, author, and date

\marginnote{\textcolor{gray}{\newthought{Each verse} consists of two lines from the verse before, and passes another two lines to the verse following. The resulting rhythm “really does remind one of the railway travel of the period”, according to fellow poet Louella Styles Vincent, writing in 1921 (\url{https://goo.gl/qTkRYT}) (‘the period’ being the 1870s). Still appropriate for recitation under one’s breath during a morning commute. More notes in this facsimile of the original (\url{https://goo.gl/6ZbzjP}).}}




\settowidth{\versewidth}{\vin Heat and the dust—they are choking,}
\begin{verse}[\versewidth]Here we are riding the rail, \\
\vin Gliding from out of the station; \\
Man though I am, I am pale, \\
\vin Certain of heat and vexation.

Gliding from out of the station, \\
\vin Out from the city we thrust; \\
Certain of heat and vexation, \\
\vin Sure to be covered with dust.

Out from the city we thrust, \\
\vin Rattling we run o’er the bridges: \\
Sure to be covered with dust, \\
\vin Stung by a thousand of midges.

Rattling we run o’er the bridges, \\
\vin Rushing we dash o’er the plain; \\
Stung by a thousand of midges, \\
\vin Certain precursors of rain.

Rushing we dash o’er the proclaiming \\
\vin Watching the clouds darkly lowering, \\
Certain precursors of rain: \\
\vin Fields about here need a showering.

Watching the clouds darkly lowering,—\\
\vin Track here is high on a bank—\\
Fields about here need a showering, \\
\vin Boy with the books needs a spank.

Track here is high on a bank, \\
\vin Just by a wretched old hovel: \\
Boy with the books needs a spank—\\
\vin “No! I don’t want a new novel!”

Just by a wretched old hovel, \\
\vin Small speck of dust in my eye. \\
“No! I don’t want a new novel!” \\
\vin—Babies beginning to cry.—Small speck of dust in my eye, \\
\vin “I will not buy papers or candy!” \\—Babies beginning to cry—\\
\vin Oh, for a tomahawk handy!

“I will not buy papers or candy!” \\
\vin Train boys deserve to be slain; \\
Oh, for a tomahawk handy! \\
\vin Oh, for the cool of the rain!

Train boys deserve to be slain, \\
\vin Heat and the dust—they are choking, \\
Oh, for the cool of the rain! \\
\vin—“Gent” just behind me is joking.

Heat and the dust they are joking, \\
\vin Clogging and filling my pores, \\—“Gent” just behind me is joking, \\
“Gent” just in front of me snores.

Clogging and filling my pores, \\
\vin Ears are on edge at the rattle; \\
“Gent” just in front of me snores, \\
\vin Sounds like the noise of a battle.

Ears are on edge at the rattle, \\
\vin Man though I am, I am pale, \\
Sounds like the noise of a battle, \\
\vin Here we are riding the rail.\end{verse}



\end{document}