\documentclass{tufte-handout}
\let\orignewcommand\newcommand  % store the original \newcommand
\let\newcommand\providecommand  % make \newcommand behave like \providecommand
\RequirePackage{verse}
\let\newcommand\orignewcommand  % use the original `\newcommand` in future
\makeatletter
% Use the original definition from verse.sty
\renewcommand*{\theHpoemline}{\arabic{verse@envctr}.\arabic{poemline}}
\makeatother

% Set up the spacing using fontspec features
% See https://groups.google.com/d/topic/tufte-latex-commits/JcgGP-1R138/discussion
   \renewcommand\allcapsspacing[1]{{\addfontfeature{LetterSpace=15}#1}}
   \renewcommand\smallcapsspacing[1]{{\addfontfeature{LetterSpace=10}#1}}

%\geometry{showframe}% for debugging purposes -- displays the margins

\usepackage{amsmath}

%%
% Prints a trailing space in a smart way.
\usepackage{xspace}

% Set the main and monospaced fonts
%
\setromanfont[Mapping=tex-text,Ligatures={Common, Rare, Discretionary},Numbers=OldStyle]{Valkyrie T3}
\setmonofont[Mapping=tex-text,Scale=MatchLowercase]{Triplicate T4c}

% Set up the images/graphics package
\usepackage{graphicx}
\setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
\graphicspath{{graphics/}}

\title{About Me}
\author{}
\date{Thursday, November 26th, 2020}  % if the \date{} command is left out, the current date will be used

% The following package makes prettier tables.  We're all about the bling!
\usepackage{booktabs}

% The units package provides nice, non-stacked fractions and better spacing
% for units.
\usepackage{units}

% The fancyvrb package lets us customize the formatting of verbatim
% environments.  We use a slightly smaller font.
\usepackage{fancyvrb}
\fvset{fontsize=\normalsize}

% Small sections of multiple columns
\usepackage{multicol}

% Provides paragraphs of dummy text
\usepackage{lipsum}

% Make hyperlinks appear as footnotes
% Taken from https://groups.google.com/forum/#!topic/pandoc-discuss/O-N0H1eBnVU
\usepackage{url}
% This bit ensures hyperlinks can have linebreaks on hyphens
% see http://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother
\renewcommand{\href}[2]{#2\footnote{\raggedright\url{#1}}}
% optionally add \itshape to get italics, or replace \rmfamily with \ttfamily
\renewcommand\UrlFont{\rmfamily\itshape}

% These commands are used to pretty-print LaTeX commands
\newcommand{\doccmd}[1]{\texttt{\textbackslash#1}}% command name -- adds backslash automatically
\newcommand{\docopt}[1]{\ensuremath{\langle}\textrm{\textit{#1}}\ensuremath{\rangle}}% optional command argument
\newcommand{\docarg}[1]{\textrm{\textit{#1}}}% (required) command argument
\newenvironment{docspec}{\begin{quote}\noindent}{\end{quote}}% command specification environment
\newcommand{\docenv}[1]{\textsf{#1}}% environment name
\newcommand{\docpkg}[1]{\texttt{#1}}% package name
\newcommand{\doccls}[1]{\texttt{#1}}% document class name
\newcommand{\docclsopt}[1]{\texttt{#1}}% document class option name

\begin{document}

\maketitle% this prints the handout title, author, and date

Hi, I’m Faiz (pronounced FEZ). I’m currently a Computing major in the \href{https://ccs.ucsb.edu}{College of Creative Studies} at UC Santa Barbara.

In the field of computer science, my current interests include scalable systems, human-centered design, and the Racket programming language. In addition to internships, my projects (past and present) include \href{https://DrDocx.com}{DrDocx},\footnote{DrDocx is a free, open source desktop application built to streamline medical practitioners workflows’ with automated report generation and intelligent analysis.} \href{https://github.com/project-anacapa/anacapa-github-linker}{a computer science education research tool}, \href{https://github.com/ProbablyFaiz/Mocktopia-Scripts}{an automated tabulation system for mock trial tournaments}, and \href{project-assets/M3-Challenge-2019-Paper.pdf}{various} \href{project-assets/GNP-Evacuation-Routes.pdf}{data science} \href{https://github.com/ProbablyFaiz/RedditPoliticalSentiment}{projects} among other things. For a full list, check out the homepage of this website.

Outside of computer science, I’m also passionate about public policy and constitutional law. My recent writing in these areas includes articles on \href{https://dailynexus.com}{religious liberty} and \href{posts/deplatforming.html}{antitrust} law. In addition, I’ve written academic analyses of \href{project-assets/climate-change-framework.pdf}{climate-oriented foreign aid plans},  \href{project-assets/third-party-doctrine.pdf}{Fourth Amendment jurisprudence} and the \href{project-assets/independent-legislature-doctrine.pdf}{independent state legislature doctrine}. I also co-founded and lead UCSB’s undergraduate moot court team, which qualified two teams to the national championship tournament this year.

This website is created with \href{https://github.com/mbutterick/pollen}{Pollen}, an open-source publishing system built in Racket. As much as I’m enjoying Racket, I can’t take credit for the incredible work done by Joel Dueck, whose \href{https://github.com/otherjoel/try-pollen}{try-pollen} project provides the bulk of the code powering this website.

If you have an interesting opportunity or good book recommendation, I’d love to \href{mailto:faiz.surani@gmail.com}{hear from you}.

\end{document}